\huge A Usability Evaluation of Tor Launcher

### 2016-10-24 pets2017-paper/pets2017-paper.tex
small word optimizations.

\section{Formative Usability Testing}
\label{sec:qualitative}
This section discusses our small-scale, qualitative usability evaluation and resulting user insights.

@@

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows 8 computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that simulated E1, E2, or E3 and started the video recording.

@@

\section{Summative Usability Testing}
\label{sec:quantitative}
This section discusses our large-scale quantitative usability evaluation and resulting user measurements.

@@

\subsection{Setup}
We ran our experiment at <Redacted lab>, an experimental social science laboratory for behavioral experiments. The testing room had 36 workstations with identical Windows~7 laptops. Side panels at each workstation to discouraged participants from looking at other participants' screens. 
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.

Before each session, we ran a script that downloaded the necessary software, set up one of the six experimental conditions, and start the video recording. Each computer was manually assigned an interface-environment combination in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition. In contrast to the previous usability test, we installed an instrumented version of Tor Browser 5.0.3 or an instrumented version of Tor Browser 5.0.3. with a redesigned configuration interface. The instrumentation in the interface logged user interactions such as window transitions, mouse clicks, and menu selections. Similarly to the previous usability test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment.

>>>>

\section{Formative Usability Testing}
\label{sec:qualitative}
This section discusses our small-scale, qualitative usability experiment and resulting user insights.

@@

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows 8 computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started the screen recording.

@@

\section{Summative Usability Testing}
\label{sec:quantitative}
This section discusses our large-scale quantitative usability experiment and resulting user measurements.

@@

\subsection{Setup}
We ran our experiment at <redacted lab>, an experimental social science laboratory for behavioral experiments. The testing room had 36 workstations with identical Windows~7 laptops. Side panels at each workstation to discouraged participants from looking at other participants' screens. 
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.

Before each session, we ran a script that downloaded the necessary software, set up one of the three simulated environments (E1, E2, or E3), and downloaded the original Tor Browser 5.0.3 or a modified version of Tor Browser 5.0.3 that contained our design changes (OLD or NEW), and start the video recording. In contrast to the previous test, we installed an instrumented versions of Tor Browser 5.0.3. The instrumentation logged user interactions, such as window transitions, mouse clicks, and menu selections. Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment. Each computer was manually assigned one of the six interface-environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
